Assessing the Global COVID19 Impact on Air Transport with Open Data

### 2021-06-09 paper.Rmd
check points for abstract inserted (as javascript comments)
a few breadcrumbs

---
title: "Assessing the Global COVID19 Impact on Air Transport with Open Data"
date: "`r format(Sys.Date(), '%d %B %Y')`"
output:
  bookdown::pdf_book:
     base_format: rticles::ieee_article
bibliography: "DASC2021.bib"
affiliation:
  ## use one only of the following
  # author-columnar: true         ## one column per author
  institution-columnar: true  ## one column per institution  
  # wide: true          ## one column wide author/affiliation fields
  institution:
    - name: EUROCONTROL
      department: Performance Review Unit
      location: Brussels (Belgium)
      #mark: 1
      author:
        - name: Rainer Koelle
          email: rainer.koelle@eurocontrol.int
    - name: DECEA
      department: tbd ... 
      location: tbd location - suggest Rio (Brazil)
      #mark: 2
      author:
        - name: Fabio Coneiro Barbarosa
          email: second_author@somedomain.com
abstract: |
  This paper approaches the impact of the pandemic as a massive service disruption of the pre-pandemic global     connectivity and regional air transport networks. In particular, the project aims to provide data analytical evidence for policy success and transformation of the air transportation system. As an aspirational goal, the industry aims to recover in a “greener” manner. The project builds on openly available data sets. The paper will be produced in a reproducible manner making the data, code, and its processing available to interested reseachers and practitioners. The open assessment will provide policy makers with a tool to assess the reaction to local or regional measures. 
---

@@

<!--| 3. Purpose and significance of the paper.  -->

@@

>>>>

---
title: "Assessing the Global COVID19 Impact on Air Transport with Open Data"
date: "`r format(Sys.Date(), '%d %B %Y')`"
output:
  bookdown::pdf_book:
     base_format: rticles::ieee_article
bibliography: "DASC2021.bib"
affiliation:
  ## use one only of the following
  # author-columnar: true         ## one column per author
  institution-columnar: true  ## one column per institution  
  # wide: true          ## one column wide author/affiliation fields
  institution:
    - name: EUROCONTROL
      department: Performance Review Unit
      location: Brussels (Belgium)
      #mark: 1
      author:
        - name: Rainer Koelle
          email: rainer.koelle@eurocontrol.int
    - name: DECEA
      department: tbd ... 
      location: tbd location - suggest Rio (Brazil)
      #mark: 2
      author:
        - name: Fabio Coneiro Barbarosa
          email: second_author@somedomain.com
abstract: |
  This paper approaches the impact of the pandemic as a massive service disruption of the pre-pandemic global     connectivity and regional air transport networks. In particular, the project aims to provide data analytical evidence for policy success and transformation of the air transportation system. As an aspirational goal, the industry aims to recover in a “greener” manner. The project builds on openly available data sets. The paper will be produced in a reproducible manner making the data, code, and its processing available to interested reseachers and practitioners. The open assessment will provide policy makers with a tool to assess the reaction to local or regional measures.
  <!-- motivation -->
  <!-- short background - why important -->
  <!-- approach chosen / research method -->
  <!-- experimental work -->
  <!-- results obtained -->
  <!-- conclusions / key take-away --> 
---

@@

<!--| 3. Purpose and significance of the paper.  -->
This paper approaches the impact of the pandemic as a massive service disruption of the pre-pandemic global connectivity and regional air transport networks. In particular, the project aims to provide data analytical evidence for policy success and transformation of the air transportation system. As an aspirational goal, the industry aims to recover in a “greener” manner. To date, no assessment of this transformational aspects has been conducted.

@@

* data-analytical approach - using open data / freely available (tbd: validated against organisational data)
* ...

### 2021-06-09 paper.tex
a few breadcrumbs

>>>>

This paper approaches the impact of the pandemic as a massive service disruption of the pre-pandemic global connectivity and regional air transport networks. In particular, the project aims to provide data analytical evidence for policy success and transformation of the air transportation system. As an aspirational goal, the industry aims to recover in a ``greener'' manner. To date, no assessment of this transformational aspects has been conducted.

\begin{itemize}
\tightlist
\item
  data-analytical approach - using open data / freely available (tbd: validated against organisational data)
\item
  \ldots{}
\end{itemize}
